Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
progress on lazy UD

\citet{siek2012interpretations} present the first \lazyD{} Blame Calculus and 
revised coercion calculi.
\todo[inline]{Not ``first''... lazy D is in the 2009 paper, right?
  Or did you mean something else? -Jeremy}
\todo[inline]{The ``Blame Calculus'' is a \lazyUD{} cast calculus.
  There is no such thing as a \lazyD{} Blame Calculus. -Jeremy}
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bisimulate the 
corresponding Blame Calculi.

@@

\subsection{The \lazyUD{} cast calculus [Jeremy]}

Fig.~\ref{fig:apply-Cast-UD}

@@

  Syntax
  \[
  \begin{array}{rclr}
    \stxrule{v}{values}{
      \cdots \mid 
      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
      \vOOcast{v}{ \cOOcast{P}{l}{P} }
    }
  \end{array}
  \]

@@

\section{Background: Normal Coercion} \label{sec:coercion-calculus}

>>>>

\citet{siek2012interpretations} present the first \lazyD{} Blame Calculus and 
revised coercion calculi.
\todo[inline]{Not ``first''... lazy D is in the 2009 paper, right?
  Or did you mean something else? -Jeremy}
\todo[inline]{The ``Blame Calculus'' is a \lazyUD{} cast calculus.
  There is no such thing as a \lazyD{} Blame Calculus. -Jeremy}
\todo[inline]{Actually, Wadler might disagree that the blame calculus is
  a lazy UD calculus... because the blame calculus has polarity in the blame
  labels, and the lazy UD calculus does not. So perhaps we should just
  say lazy UD cast calculus, and explain that it is very close to the
  blame calculus. -Jeremy}
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bisimulate the 
corresponding Blame Calculi.

@@

\subsection{The Blame Calculus (i.e. \lazyUD{} cast calculus) [Jeremy]}

The dynamic semantics of the Blame Calculus, which we define here as a
CEK machine, is similar to that of the \lazyD{} cast calculus
(Fig. \ref{machine-cekc}). The only difference is in the definition of
the $\mathit{applyCast}$ function, in which a cast whose source or
target is the unknown type $\star$ is always split into two casts that
go through an injectiable type, that is, a type in which all
sub-components are the unknown type, such as $\star \to \star$. The
definition of $\mathit{applyCast}$ for the Blame Calculus is given in
Fig.~\ref{fig:apply-Cast-UD}.

@@

  Syntax
  \[
  \begin{array}{rclr}
     \stxrule{I}{injectable types}{
		\POOfun{\star}{\star} \mid \POOunit \mid \star \times \star \mid \star + \star}
    \stxrule{v}{values}{
      \cdots \mid 
      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
      \vOOcast{v}{ \cOOcast{P}{l}{P} }
    }
  \end{array}
  \]

@@

\subsection{Coercions in Normal Form} \label{sec:coercion-calculus}
